Human Capital Model

### 2016-02-01 Tex/paper.tex
tt

In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, and they are time-dependant functions. It takes several steps to calculate them.

@@

Our strategy focus on two variables, $v_h$ and $u_h$. Nine pairs of data are tested to find the best strategy.
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
      &$v_h$  &$u_h$        \\ \hline
 1    &0.1             & 50              \\ \hline
 2    &0.2             & 50              \\ \hline
 3    &0.3             & 50              \\ \hline
 4    &0.1             & 40              \\ \hline
 5    &0.2             & 40              \\ \hline
 6    &0.3             & 40              \\ \hline
 7    &0.1             & 30              \\ \hline
 8    &0.2             & 30              \\ \hline
 9    &0.3             & 30              \\ \hline
\end{tabular}
\end{center}

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}
\begin{itemize}
\item We change the shape of the bathtub to sphere and cylinder with the same strategy. The temperature graph shows that sphere is the properest shape for keeping water temperature. The cylinder is proved to be the worst on keeping temperature. However, temperature of cylinder bathtub is evener than others.
\item We change the volume of the bathtub without changing the proportion. The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
\end{itemize}

\subsection{Parameters of Person}
\label{sec:parameters of person}
\begin{itemize}
\item
\item
\item
\end{itemize}

\subsection{Effects of Motion}
\label{sec:effects of motion}
When the person in the bathtub makes motions, the heat exchange coefficient between the person and water ${\gamma}_2$ increases. That means heat exchange between water and the person increases. In another aspect, the air above flows, so that evaporation heat of water increases. Water loses more heat.

The effect is that more heat is needed to keep the temperature, consequently $u_h$ as the best strategy increases to keep the temperature.

\subsection{Effects of Bubble Bath Additive}
\label{sec:effects of bubble bath additive}
When bubble bath additive is added while initially filling the bathtub, bubbles stay on the surface and the evaporation of water to air is limitted. So water loses less heat.

The effect is that less heat is needed to keep the temperature. So $u_h$ for best strategy decreases to keep the temperature.

@@

\begin{itemize}
\item Our model make good use of thermology knowledge so it can reflect the situation in the real world realistically.
\item Our model build a 3D geometry to simulate the research object so
\item The network we built includes both microcosmic part and
  macrocosmic part, and they react to each other.
\item Our model proves the effect of time.
\end{itemize}

>>>>

In the equation above, $u_3$ is temperature of bathtub, we assume it is unchangeable and as same as initial air temperature.

While $u_1$ i, the temperature of air, is time-dependant, because water vapor transfer heat to air. We can calculate $u_1$ by calculating the energy of water vapor evaporated in the air. Referencing the deduction of evaporation in the last section,  
\begin{equation}
  u_1=u_0+\frac{{C_w}\rho}{{C_a}{{\rho}_a}(x_s-x_0)(1-e^{-\lambda t})
\end{equation}

@@

Our strategy focus on two variables, $v_h$ and $u_h$. Nine pairs of data are tested to find the best strategy.
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
      &$v_h$  &$u_h$        \\ \hline
 1    &0.1             & 50              \\ \hline
 2    &0.2             & 50              \\ \hline
 3    &0.3             & 50              \\ \hline
 4    &0.1             & 40              \\ \hline
 5    &0.2             & 40              \\ \hline
 6    &0.3             & 40              \\ \hline
 7    &0.1             & 30              \\ \hline
 8    &0.2             & 30              \\ \hline
 9    &0.3             & 30              \\ \hline
\end{tabular}
\end{center}
In each operation, $u_2$ is taken as $33.5^{\circ}\mathrm$ and the initial value condition is $u=35^{\circ}\mathrm$. Then the result performs like this []

Comparing the temperature distribution of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}
\begin{itemize}
\item We change the shape of the bathtub to sphere and elliptical with the same strategy. The temperature graphic shows that sphere is the most proper shape for keeping water temperature. Square performs the worst on keeping temperature. However, temperature of square bathtub is more evenly than others.
\item We change the volume of the bathtub without changing the proportion. The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increased as volume increases.
\end{itemize}

\subsection{Parameters of Person}
\label{sec:parameters of person}
\begin{itemize}
\item Comparing the temperature graph with different shape of the person, we found when the shape gets more regular, $u_h$, $v_h$ becomes decreases relatively.
\item The larger the person, the more heat between water and the person. That means more heat is called for. $u_h$, $v_h$ for best strategy increases.
\item When the surface temperature of the person increases, it becomes more closed to water temperature. Then water and person have less heat exchange. Less heat of hot water from faucet is called for. $u_h$, $v_h$ for best strategy decreases.
\end{itemize}

\subsection{Effects of Motion}
\label{sec:effects of motion}
When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases. That means heat exchange between water and person increases. In another aspect, the air above flow, so that evaporation heat of water increases. Water losses more heat.

The effect is that more heat is called for to keep the temperature. So $u_h$ increases for best strategy to keep the temperature.

\subsection{Effects of Bubble Bath Additive}
\label{sec:effects of bubble bath additive}
When bubble bath additive is added while initially filling the bathtub, bubble stay on the surface and restraint the evaporation of water to air. So water losses less heat.

The effect is that less heat is called for to keep the temperature. So $u_h$ decreases for best strategy to keep the temperature.

@@

\begin{itemize}
\item Our model make good use of thermology knowledge so it can reflect the situation in the real world realistically.
\item Our model build a 3D geometry to simulate the research object so
\item The network we built include both microcosmic part and
  macrocosmic part, and they react to each other.
\item Our model proves the effect of time.
\end{itemize}
